Contextual Combinatorial Cascading Bandits

### 2016-01-08 contextual combinatorial cascading bandits.tex
modify
update a result

@@

@@

>>>>

Combinatorial multi-armed bandit(MAB) problem has been studied extensively in statistics and machine learning.

@@

Stochastic online learning with combinatorial actions has been studies with semi-bandit feedback \cite{chen2013combinatorial}.

@@

\section{Experiments}

\section{Conclusions}

In this paper, we propose contextual combinatorial cascading bandits, a class of contextual combinatorial bandits with partial observations.
